---
title: "replication"
author: "Nick F & Aaron K"
date: "February 24, 2015"
output: html_document
---

```{r echo = FALSE}

#load packages
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(ggplot2))
suppressPackageStartupMessages(require(foreign))
suppressPackageStartupMessages(require(aod))
suppressPackageStartupMessages(require(lsr))

Sem <- function(x) {
  #creates the function to calculate standard error of the mean
  sqrt(var(x)/length(x))
  }

```

# Study 1a
> In this study, there were 103 participants (mean age = 29.3 years; 44 females, 59 males; median household size = 3 people; median household income = $35,000)...One participant was excluded as an outlier on income (more than 3 SD from the mean). 

```{r echo = FALSE}

# detect the user's directory:
directory  <- "C:/Users/Nick/Documents/Github/scarcityvalueRep"
if (Sys.getenv('USER')=="air") directory <- "~/Dropbox/SOC504/replicate"
setwd(directory)

# read in the data for 1a using the spss and the csv file
# the warning/messages suppressed; the data imports cleanly.
suppressMessages(suppressWarnings(raw_1a_spss <- read.spss("framing/study_1a.sav", to.data.frame = TRUE)))
suppressMessages(suppressWarnings(raw_1a_csv <- read.csv("study_1a_demog.csv", header = FALSE)))

#calculate mean age
raw_1a_csv %>%
  summarise(average_age = mean(V3)) %>%
  round(digits = 1)

#calculate sex breakdown
raw_1a_csv %>%
  group_by(V4) %>%
  summarise(sex_breakdown = n())

#calculate sample size, median household income, median household size
raw_1a_spss %>%
  summarise(sample.size = n(), median.household.income = median(income2), median.household.size = median(house))

```
***Results***
-----

> We conducted binary logistic regressions to compare how frequently partici- pants cited each of the two considerations of interest (trade-offs vs. location) as a function of income. Higher-income participants were more likely than lower-income participants to name location as the main consideration, β = 2.52, Wald-test χ2(1, N = 102) = 5.54, p < .05,

```{r echo = FALSE}

# removes the 1 removed observation for being 3 SDs away from the mean.
clean_1a <- raw_1a_spss %>%
  filter(filter_. != "Not Selected")

#run logistic regression and print summary (location thinking)
logit1logses <- glm(location ~ logses, data = clean_1a, family = "binomial")
summary(logit1logses)

#run wald test using the output from logit1logses
wald.test(b = coef(logit1logses), Sigma = vcov(logit1logses), Terms = 2)
```

> but lower-income participants were more likely than higher- income participants to name trade-offs as the main con- sideration, β = −1.62, Wald-test χ2(1, N = 102) = 4.67, p <.05...

```{r echo = FALSE}

#run logisitic regression and print summary (trade-off thinking)
logit2logses <- glm(tradeoff ~ logses, data = clean_1a, family = "binomial")
summary(logit2logses)

#run wald test using the output from logit2logses
wald.test(b = coef(logit2logses), Sigma = vcov(logit2logses), Terms = 2)
```


```{r echo = FALSE}

#create dataframe with new mutated variables for low income
figure1alow <- clean_1a %>%
  filter(income2 <= 35000) %>%
  mutate(total.n = n(), total.tradeoff = sum(tradeoff), prop.tradeoff = sum(tradeoff)/n(), total.location = sum(location), prop.location = sum(location)/n(), SE.tradeoff = sqrt(prop.tradeoff * (1 - prop.tradeoff)/total.n), CI.tradeoff = qnorm(.975) * SE.tradeoff, SE.location = sqrt(prop.location * (1 - prop.location)/total.n), CI.location = qnorm(.975) * SE.location) %>%
  distinct(prop.tradeoff, prop.location, CI.tradeoff, CI.location)

#create dataframe with new mutated variables for high income
figure1ahigh <- clean_1a %>%
    filter(income2 > 35000) %>%
  mutate(total.n = n(), total.tradeoff = sum(tradeoff), prop.tradeoff = sum(tradeoff)/n(), total.location = sum(location), prop.location = sum(location)/n(), SE.tradeoff = sqrt(prop.tradeoff * (1 - prop.tradeoff)/total.n), CI.tradeoff = qnorm(.975) * SE.tradeoff,  SE.location = sqrt(prop.location * (1 - prop.location)/total.n), CI.location = qnorm(.975) * SE.location) %>%
  distinct(prop.tradeoff, prop.location, CI.tradeoff, CI.location)

#figure 1a data frame
title = factor(c("trade-offs", "location"), levels = c("trade-offs", "location"))
values = c(figure1alow$prop.tradeoff, figure1alow$prop.location, figure1ahigh$prop.tradeoff, figure1ahigh$prop.location)
income = c("lower income", "lower income", "higher income", "higher income")
CIs = c(figure1alow$CI.tradeoff, figure1alow$CI.location, figure1ahigh$CI.tradeoff, figure1ahigh$CI.location)
fig1a.table <- data.frame(title, values, income, CIs)
income <- factor(fig1a.table$income, levels = c("lower income", "higher income"))

#produces figure 1a
figure1a <- fig1a.table %>%
  ggplot(aes(x = title, y = values, fill = income)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("Proportion Endorsing Reason") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1a - the proportion of lower- and higher-income participants\nciting trade-off and location considerations in Study 1a\n(error bars represent 95% confidence interval)") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

#displays figure 1a
print(figure1a)

```


# Study 1b - Consistent Valuations Under Scarcity


In Study 1b, there were 151 participants (mean age = 32.9 years; 76 females, 75 males; median household size = 3 people, median household income = $45000).  In Study 1c, there were 604 participants (mean age = 29.9 years; 246 females, 358 males; median household size = 2 people; median household income = $45,000).  Study 1d was conducted with a large, representative sample drawn from Survey Sampling International's panel of U.S respondents.  There were 2,015 participants (mean age = 39.1 years; 1,022 females, 993 males; median household size = 3 people; median household income = $55,000).  In Study 1b, participants read the beer-on-the-beach scenario and indicated their WTP for the beer.  Studies 1c and 1d directly replicated Study 1b.  Because WTP was elicited with an open-ended scale, some participants named unreasonably high prices.  We describe our exclusion rules for these responses in the next section.  These rules were determined before we conducted the significance tests.

```{r echo = FALSE}

#read in the data for 1b using the spss file - the warning that comes up is okay - the data imports cleanly.
suppressMessages(suppressWarnings(raw_1b_spss <- read.spss("framing/study_1b.sav", to.data.frame = TRUE)))
suppressMessages(suppressWarnings(raw_1b_csv <- read.csv("study_1b_demog.csv", header = TRUE)))

#average age for Study 1b
raw_1b_csv %>%
  filter(Age != "NA") %>%
  summarise(average_age = mean(Age)) %>%
  round(digits = 1)

#calculate sex breakdown for Study 1b
raw_1b_csv %>%
  filter(Gender != 75, Gender != 76) %>%
  group_by(Gender) %>%
  summarise(sex_breakdown = n())

raw_1b_spss %>%
  summarise(sample.size = n(), median.household.income = median(income2), median.household.size = median(house))
```

***Results***
-----
In Study 1b, 2 participants were excluded whose Willing-to-pay (WTP) was more than 3 standard deviations from the mean.

Higher-income participants showed the classic effect, offering a higher price for beer from the resort

```{r echo = FALSE}

clean_1b <- raw_1b_spss %>%
  filter(filter_. != "Not Selected")

clean_1b %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates high-income WTP beer price at resort - summarise to display in print-out

clean_1b_high_resort <- clean_1b %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for high income participants in the resort scenario - to use in figure 1b

```
compared to the grocery store.

```{r echo = FALSE}
clean_1b %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates high-income WTP beer price at grocer - summarise to display in print-out

clean_1b_high_grocer <- clean_1b %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for high income participants in the grocer scenario - to use in figure 1b
```
But lower income participants' WTP did not differ significantly between beer from the resort

```{r echo = FALSE}
clean_1b %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates low income WTP beer price at resort

clean_1b_low_resort <- clean_1b %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for low income participants in the resort scenario - to use in figure 1b
```
 and beer from the store.
 
```{r echo = FALSE}
clean_1b %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates low income WTP beer price at grocery store

clean_1b_low_grocer <- clean_1b %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for low income participants in the grocer scenario - to use in figure 1b
```

The interaction between income and context was significant F(1,145) = 11.18, p < 0.01, eta squared partial = 0.07.
```{r echo = FALSE}
aov_1b <- aov(beer ~ resort * split, data = clean_1b)
summary(aov_1b)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1b, type = 2, anova = FALSE)
```
The interaction was also significant when income was treated as a continuous variable beta = 2.27 (the closest I could replicate from the data was 2.67), t(145) = 2.17, p < 0.05.

```{r echo = FALSE}
lm1 <- lm(beer ~ resort * logses, data = clean_1b)
summary(lm1)
```

```{r echo = FALSE}

title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1b_low_grocer$mean.beer, clean_1b_high_grocer$mean.beer, clean_1b_low_resort$mean.beer, clean_1b_high_resort$mean.beer)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1b_low_grocer$CI, clean_1b_high_grocer$CI, clean_1b_low_resort$CI, clean_1b_high_resort$CI)
fig1b.table <- data.frame(title, values, location, CIs)
#figure 1b data frame

figure1b <- fig1b.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1b - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1b\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1b

print(figure1b)
#displays figure 1b

```

-----
-----
#Study 1c


We replicated the results of 1b with larger samples in studies 1c and 1d.  In study 1c, we excluded 2 participants with missing responses, 5 with unreasonably high WTPs (over $100), and 19 additional outliers on WTP, which left 578 participants.

```{r echo = FALSE}

#read in the data for 1c using the spss file - the warning that comes up is okay - the data imports cleanly.
suppressMessages(suppressWarnings(raw_1c_spss <- read.spss("framing/study_1c.sav", to.data.frame = TRUE)))
suppressMessages(suppressWarnings(raw_1c_csv <- read.csv("study_1c_demog.csv", header = TRUE)))

#average age for Study 1c
raw_1c_csv %>%
  filter(age != "NA") %>%
  summarise(mean.age = mean(age)) %>%
  round(digits = 1)

#calculate sex breakdown for Study 1c
raw_1c_csv %>%
  filter(gender != "NA") %>%
  group_by(gender) %>%
  summarise(sex_breakdown = n())

#calculate total sample size for Study 1c
raw_1c_csv %>%
  summarise(sample.size = n())

#calculate median household income and size for Study 1c
raw_1c_spss %>%
  summarise(median.household.income = median(inc2), median.household.size = median(house))

clean_1c <- raw_1c_spss %>%
  filter(filter_. != "Not Selected")
```
***Results***
-----

Dividing participants according to a median split on income, we found that higher-income participants offered a higher price for beer from the resort

```{r echo = FALSE}
clean_1c %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.beer = mean(pay), ci.low = mean(pay) -  (1.96 * Sem(pay)), ci.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_high_resort <- clean_1c %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for high income participants in the resort scenario - to use in figure 1c

```
than for beer from the grocery store:

```{r echo = FALSE}
clean_1c %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.beer = mean(pay), ci.low = mean(pay) -  (1.96 * Sem(pay)), ci.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_high_grocer <- clean_1c %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for high income participants in the grocer scenario - to use in figure 1c

```

Lower-income participants' WTP did not differ significantly between beer from the resort,

```{r echo = FALSE}
clean_1c %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.beer = mean(pay), ci.low = mean(pay) -  (1.96 * Sem(pay)), ci.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_low_resort <- clean_1c %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for low income participants in the resort scenario - to use in figure 1c

```
and beer from the store.

```{r echo = FALSE}
clean_1c %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.beer = mean(pay), ci.low = mean(pay) -  (1.96 * Sem(pay)), ci.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_low_grocer <- clean_1c %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for low income participants in the grocer scenario - to use in figure 1c

```

The interaction between income and context was significant, F(1,574) = 5.68, p < 0.05, eta squared partial = 0.01.

```{r echo = FALSE}
aov_1c <- aov(pay ~ resort * split, data = clean_1c)
summary(aov_1c)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1c, type = 2, anova = FALSE)
```

The interaction was also significant when income was treated continuously, beta = 1.65 **(the closest I could replicate was 2.03)**, t(574) = 3.27, p < 0.01.

```{r echo = FALSE}
lm2 <- lm(pay ~ resort * logses, data = clean_1c)
summary(lm2)
```

```{r echo = FALSE}

title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1c_low_grocer$mean.pay, clean_1c_high_grocer$mean.pay, clean_1c_low_resort$mean.pay, clean_1c_high_resort$mean.pay)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1c_low_grocer$CI, clean_1c_high_grocer$CI, clean_1c_low_resort$CI, clean_1c_high_resort$CI)
fig1c.table <- data.frame(title, values, location, CIs)
#figure 1c data frame

figure1c <- fig1c.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1c - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1c\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1c

print(figure1c)
#displays figure 1c

```

-----
-----
#Study 1d

```{r echo = FALSE}
setwd("framing")
raw_1d_spss <- read.spss("study_1d.sav", to.data.frame = TRUE)
#reads the data for study 1d

clean_1d <- raw_1d_spss %>%
  filter(filter_. != "Not Selected")
```

In Study 1d (the nationally representative sample), a large number of participants reported unreasonably high WTPs, and exclusions based on the rules set for the smaller samples in previous studies would have left many unreasonable prices in the data set.  We therefore included in our analyses only those participants with a WTP of $20 or less, which seemed like the upper bound of a reasonable price.  This set a cutoff price similar to the cutoff price based on the stand deviations in Studies 1b and 1c. After this exclusion and the exclusion of 4 additional participants who were outlines on income, the final sample included 1,898 participants.  

***Results***
-----

Dividing participants according to a median split on eincome, we found that higher-income participants offered a higher price for feer from the resort (M = $6.80, 95% CI [$6.41, $7.18])

```{r echo = FALSE}
clean_1d %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_high_resort <- clean_1d %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```
than for beer from the grocery store (M = $5.46, 95% CI [$5.13, $5.79]).

```{r echo = FALSE}
clean_1d %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_high_grocer <- clean_1d %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)

```

Lower-income participants' WTP did not differ significantly between the resort (M = $6.21, 95% CI [$5.83, $6.60])

```{r echo = FALSE}
clean_1d %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_low_resort <- clean_1d %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

and the store (M = %5.71, 95% CI [$5.31, $6.11]).

```{r echo = FALSE}
clean_1d %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_low_grocer <- clean_1d %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

The interaction between income and context was significant, F(1, 1984) = 4.82, p < 0.05, eta squared partial = 0.003. (SEE FIGURE 1d)

```{r echo = FALSE}
aov_1d <- aov(wtp ~ resort * split, data = clean_1d)
summary(aov_1d)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1d, type = 2, anova = FALSE)

```

This interaction was marginally significant when income was treated continuously, beta = 0.50 **(the closest I could replicate was 0.93)**, t(1894) = 1.85, p < 0.07.

```{r echo = FALSE}
lm3 <- lm(wtp ~ resort * logses, data = clean_1d)
summary(lm3)
```


```{r echo = FALSE}

title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1d_low_grocer$mean.wtp, clean_1d_high_grocer$mean.wtp, clean_1d_low_resort$mean.wtp, clean_1d_high_resort$mean.wtp)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1d_low_grocer$CI, clean_1d_high_grocer$CI, clean_1d_low_resort$CI, clean_1d_high_resort$CI)
fig1d.table <- data.frame(title, values, location, CIs)
#figure 1c data frame

figure1d <- fig1d.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1d - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1d\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1d

print(figure1d)
#displays figure 1d

```


The beer-on-the-beach scenario provides a canonical example of the difficulty people have in translating utility into value.  People have a sense of how much they would enjoy the beer, but they have difficulty representing this enjoyment with a price.  However, under conditions of scarcity, people base their price not merely on anticipated enjoyment, but also on anticipated trade-offs, and those are more consistent guides for valuation.  Could scarcity also lead to more consistent baluation of a dollar itself? The next set of studies addressed this question.

-----
-----

#Study 2a - Proportional Versus Trade-Off Thinking

```{r echo = FALSE}
setwd("framing")
raw_2a_spss <- read.spss("study_2a.sav", to.data.frame = TRUE)
#reads the data for study 2a
```

In Study 2a, there were 238 participants ((we are unable to replicate mean age, gender split, median household size, or median household income due to that data not being in the public dataset)) Median ses (which is income / sqrt(householdsize)):

```{r echo = FALSE}
raw_2a_spss %>%
  summarise(sample.size = n(), median.ses = median(ses))

```

***Results***
-------

One participant was excluded as an outlier on income.

```{r echo = FALSE}

clean_2a <- raw_2a_spss %>%
  filter(filter_. != "Not Selected")
```

We conducted binary logistic regressions to comepare the frequency with which participants cited each of the two considerations of interest (trade-offs vs proportional discount) as a function of income.  Higher-income participants were more likely than lower-income participants to use proportional thinking, beta = 0.87, Wald-test chi square (1, N = 237) = 4.02, p < 0.05.

```{r echo = FALSE}

logit3logses <- glm(context ~ lgses, data = clean_2a, family = "binomial")
summary(logit3logses)

wald.test(b = coef(logit3logses), Sigma = vcov(logit3logses), Terms = 2)
```

but lower-income participants were more likely than higher-income participants to use trade-off thinking, beta = -0.96, Wald-test chi square (1, N = 237) = 4.69, p < 0.05.

```{r echo = FALSE}

logit4logses <- glm(tradeoff ~ lgses, data = clean_2a, family = "binomial")
summary(logit4logses)

wald.test(b = coef(logit4logses), Sigma = vcov(logit4logses), Terms = 2)
```

This again suggests that scarcity leads people to generate their own comparison standards, and Studies 2b through 2d tested whether this leads to more consistent preferences.

#Study 2b - Valuing Discounts

```{r echo = FALSE}

clean_2b %>%
  filter(split == 0, cond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2b %>%
  filter(split == 0, cond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)

```

The ineraction between income and context was significant in a binary logistic regression, beta = -0.048, Walt-test chi square (1, N = 702) = 4.93, p < 0.05,

```{r echo = FALSE}

logit5logses <- glm(go ~ split * cond, data = clean_2b, family = "binomial")
summary(logit5logses)

wald.test(b = coef(logit5logses), Sigma = vcov(logit5logses), Terms = 4)
```

and was marginally significant when income was treated continuously, beta = -0.57, Wald-test chi square(1, N - 702) = 3.32, p < 0.07.

```{r echo = FALSE}

logit6logses <- glm(go ~ logses * cond, data = clean_2b, family = "binomial")
summary(logit6logses)

wald.test(b = coef(logit6logses), Sigma = vcov(logit6logses), Terms = 4)
```

###Study 2c

Five participants were excluded for missing responses in Study 2c, so 1,893 participants were included in the analyses.

```{r echo = FALSE}

setwd("framing")
raw_2c_spss <- read.spss("study_1d.sav", to.data.frame = TRUE)
#reads the data for study 2c

clean_2c <- raw_1d_spss %>%
  filter(filter_. != "Not Selected", go != "NA")
```

Analyses based to a median split on income revealed a more muted trend than in the previous study.  Among higher-income participants, 71%, 67%, and 51% were willing to travel when the tablet cost $300, $500, and $1,000, respectively;

```{r echo = FALSE}
clean_2c %>%
  filter(split == 1, webercond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 1, webercond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 1, webercond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

among lower-income participants, the corresponding percentages were 70%, 69%, and 55%.

```{r echo = FALSE}
clean_2c %>%
  filter(split == 0, webercond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 0, webercond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 0, webercond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

When income was treated continuously, the interaction between income and context was clear, beta = -0.39, Wald-test chi square(1, N = 1,893) = 6.13, p < 0.05.

```{r echo = FALSE}

logit7logses <- glm(go ~ logses * webercond, data = clean_2c, family = "binomial")
summary(logit7logses)

```

# Study 6
> In Study 6, 74 participants (mean age = 32.0 years; 46 females, 28 males) were...
```{r echo=F}
df.6.demo <- read.csv("csv_files/6_demo.csv", header=T)
str(df.6.demo)
mean(df.6.demo$Age)
```

