---
title: "replication2"
author: "Nick F & Aaron K"
date: "March 12, 2015"
output: html_document
---

---
```{r echo = FALSE}
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(tidyr))
suppressPackageStartupMessages(require(aod)) # wald.test
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(ggplot2))

Sem <- function(x) {
  #creates the function to calculate standard error of the mean
  sqrt(var(x)/length(x))
  }

# detect the user's directory:
directory  <- "C:/Users/Nick/Documents/Github/scarcityvalueRep/framing"
if (Sys.getenv('USER')=="air") directory <- "~/Dropbox/SOC504/replicate"
setwd(directory)

```

*Note: headlines were added to some sheets (csv), i.e. assumptions made*

---

#### Study 2d :
> In Study 2d, there were 301 participants (mean age = 30.2 years; 120 females, 181 males; median household size = 3 people; median household income = $25,000).

```{r echo=F}
# Read data in
df2d_1 <- read.csv("csv_files/2d_Sheet1.csv", header=T)
df2d_2 <- read.csv("csv_files/2d_Sheet2.csv", header=T)
```

```{r echo=F}
# Number of subjects
df2d_1 %>%
  select(subject) %>%
  summarise(n())

# Mean age
df2d_2 %>%
  summarise(mean(age, na.rm=T)) %>%
  round(digits=1)

# Number of females vs. males
df2d_2 %>%
  group_by(gender) %>%
  summarise(n())
```

Attempt to replicate median household size was complex:
```{r}
# Median Household Size
# calculated using income2 : doesn't match
df2d_1 %>%
  summarize(median(inc2, na.rm=T))
# calculated using ses : doesn't match
df2d_1 %>%
  summarize(median(ses, na.rm=T)) %>%
  round(digits=0)
# calculated using income (converted) then inverted : matches!
df2d_1 %>%
  summarize(median(income, na.rm=T))
df2d_1 %>%
  select(inc2) %>%
  distinct() %>%
  arrange(inc2) %>%
  slice(3) # '3' derived from above
# Note above: (technical) I tried to, but couldn't figure out how to use a variable instead of explicitly using the value 3. Again, I suspected the median was taken from the categorized income and then backward matched to its raw value. I suspect this is erroneous and probably due to disregarding the categorical value of 0 is meaningful.
```

> Results: We regressed willingness to travel on income (categorized by a median split), proportional size of the discount (large vs. small), absolute size of the discount ($10 vs. $150), all two-way interaction terms, and the three-way interaction term. 

```{r eval=F}
# Regression
glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")
```

Assumptions:

* willingness = 'go'
* income with median split = 'split'
* proportionate discount = 'lgdiscount'
* abs size discount = 'lgsavings'

> Higher-income participants were significantly more willing to travel for a proportionally larger discount (60%) than for a proportionally smaller discount (41%), but this was not true for lower-income participants (50% vs. 61%). 

```{r echo=FALSE}
# high-income & proportionately larger discount
df2d_1 %>%
  filter(split == 1, lgdiscount == 0) %>%
  summarise(high_prop_large = (sum(go) / n()) * 100) %>%
  round(digit=0)

# high-income & proprotionately smaller discount
df2d_1 %>%
  filter(split == 1, lgdiscount == 1) %>%
  summarise(high_prop_small = (sum(go) / n()) * 100) %>%
  round(digit=0)

# low-income & proprotionately larger discount
df2d_1 %>%
  filter(split == 0, lgdiscount == 0) %>%
  summarise(high_prop_large = (sum(go) / n()) * 100) %>%
  round(digit=0)

# low-income & proprotionately smaller discount
df2d_1 %>%
  filter(split == 0, lgdiscount == 1) %>%
  summarise(high_prop_small = (sum(go) / n()) * 100) %>%
  round(digit=0)
```

> The interaction between proportional discount and income was significant, β = −1.90, Wald-test χ2(1, N = 301) = 4.11, p < .05. 

```{r echo=F}
temp.model <- glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")

# β (beta), p
glm(go ~ split*lgdiscount*lgsavings, 
    data = df2d_1, family = "binomial") %>% 
  tidy() %>%
  filter(term == "split:lgdiscount") %>%
  mutate(β = round(estimate, digit = 2),
         p = round(p.value, digit = 2)) %>%
  select(term, β, p)

# wald test
print(wald.test(b = coef(temp.model), 
                Sigma = vcov(temp.model), 
                Terms = 5)$result$chi2[1], digit = 3)
```

> Note that this interaction did not depend on the absolute amount of the discount, as the three-way interaction was not significant, β = −0.89, Wald-test χ2(1, N = 301) = 0.28, p > .6. 

```{r echo=F}
temp.model <- glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")

# β (beta), p
glm(go ~ split*lgdiscount*lgsavings, 
    data = df2d_1, family = "binomial") %>% 
  tidy() %>%
  filter(term == "split:lgdiscount:lgsavings") %>%
  mutate(β = round(estimate, digit = 2),
         p = round(p.value, digit = 4)) %>%
  select(term, β, p)

# wald test
print(wald.test(b = coef(temp.model), 
                Sigma = vcov(temp.model), 
                Terms = 8)$result$chi2[1], digit = 3)
```

> When income was treated continuously, the interaction between proportional discount and income also emerged, but was not significant, β = −2.13, Wald-test χ2(1, N = 301) = 2.21, p < .15.

**^ Failed to replicate**

```{r echo=F, eval=F}
## Gaussian link function:
# instead of split, use income : doesn't match
tidy(glm(go ~ income*lgdiscount*lgsavings, data = df2d_1, family = "gaussian"))[5,]
# instead of split, use inc2 : doesn't match
tidy(glm(go ~ inc2*lgdiscount*lgsavings, data = df2d_1, family = "gaussian"))[5,]
# instead of split, use ses : doesn't match
tidy(glm(go ~ ses*lgdiscount*lgsavings, data = df2d_1, family = "gaussian"))[5,]

## Tried Binomial link function: 
# instead of split, use income : doesn't match
tidy(glm(go ~ income*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]
# instead of split, use inc2 : doesn't match
tidy(glm(go ~ inc2*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]
# instead of split, use ses : doesn't match
tidy(glm(go ~ ses*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]

## Random attempt:
# p matches : 0.145, but nothing else
tidy(glm(go ~ inc2:lgdiscount, data = df2d_1, family = "gaussian"))

# wald test : haven't because I don't know which model to use
```

---

#### Study 3 : incomplete

---

#### Study 4 : incomplete

---

#### Study 5 : incomplete

---

#### Study 6 : incomplete
> In Study 6, 74 participants (mean age = 32.0 years; 46 females, 28 males) were...

```{r echo=F}
df.6.demo <- read.csv("csv_files/6_demo.csv", header=T)
df.6.raw <- read.csv("csv_files/6_raw.csv", header=T)

# Number of subjects
df.6.demo %>%
  select(Subject) %>%
  summarise(n())

# Mean age
df.6.demo %>%
  summarise(mean(Age, na.rm=T))

# Number of females vs. males
df.6.demo %>%
  group_by(Gender) %>%
  summarise(n())
```

> One participant was excluded because of a computer malfunction during the game. Time-rich participants rated the loss as more expensive when they thought about a small account (M = 8.31, 95% CI = [7.78, 8.84]) than when they thought about a large account (M = 6.50, 95% CI = [5.42, 7.58]), whereas time-poor participants’ evaluations did not differ between the small-account condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large- account condition (M = 8.83, 95% CI = [7.97, 9.69]). A 2 (scarcity condition) × 2 (account condition) analysis of variance revealed a significant interaction, F(1, 69) = 5.16, p < .05, ηp2 = .07.

```{r}
# Number of subjects, filter our Subject 16 (deduced from spss filter)
df.6.edit <- df.6.raw %>%
  filter(Subject!='16')
df.6.edit %>%
   summarise(n_distinct(Subject)) 

# Total points per Subject
df.6.edit <- df.6.edit %>%
  group_by(Subject) %>%
  mutate(Total.Points=sum(Points)) %>%
  select(Subject, Cond, Total.Points) %>%
  distinct()

# Change variable to factos
df.6.edit$Subject <- as.factor(df.6.edit$Subject)
df.6.edit$Cond <- as.factor(df.6.edit$Cond)

# Add columns for different conditions: scarcity/account 

```

