---
title: "replication"
author: "Nick F & Aaron K"
date: "March 15, 2015"
output: html_document
---

```{r echo = FALSE}
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(tidyr))
suppressPackageStartupMessages(require(aod)) # wald.test
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(lsr)) #etaSquared
suppressPackageStartupMessages(require(ggplot2))

# detect the user's directory:
directory  <- "C:/Users/Nick/Documents/Github/scarcityvalueRep/framing"
if (Sys.getenv('USER')=="air") directory <- "~/Dropbox/SOC504/replicate"
setwd(directory)

# Function : calculates standard error of the mean
Sem <- function(x) {
  sqrt(var(x)/length(x))
  }

# Function : to generate mean and confidence interval & name
Mean_CI <- function(title, x){
  print(title, quote=F)
  # print Mean
  M <- t.test(x) %>%
    .$estimate %>%
    round(digits = 2) %>%
    .[[1]]
  print(c("M:", M), quote = F)
  # print Confidence Interval 95%
  CI <- t.test(x) %>%
    .$conf.int %>%
    round(digits = 2) %>%
    .[1:2]
  print(c("CI : ", CI), quote = F)
}
```

*Note: headlines were added to some sheets (csv), i.e. assumptions made*

---

# Study 1a

> In this study, there were 103 participants (mean age = 29.3 years; median household size = 3 people; median household income = $35,000)...One participant was excluded as an outlier on income (more than 3 SD from the mean). We conducted binary logistic regressions to compare how frequently partici- pants cited each of the two considerations of interest (trade-offs vs. location) as a function of income...

*We were unable to replicate sex breakdown and mean age of participants as this data was not provided in the released dataset.*

```{r echo = FALSE}
# Data import
###### detect the user's directory:
directory  <- "C:/Users/Nick/Documents/Github/scarcityvalueRep/framing"
if (Sys.getenv('USER')=="air") directory <- "~/Dropbox/SOC504/replicate/framing"
setwd(directory)

# read in the data for 1a using the spss file
# the warning/messages suppressed; the data imports cleanly.
suppressMessages(suppressWarnings(raw_1a_spss <- read.spss("study_1a.sav", to.data.frame = TRUE)))

raw_1a_spss %>%
  summarise(sample.size = n(), median.household.income = median(income2), median.household.size = median(house))
# removes the 1 removed observation for being 3 SDs away from the mean.
clean_1a <- raw_1a_spss %>%
  filter(filter_. != "Not Selected")
# count number of participants who answered 'tradeoff' or 'location' for 1a.
raw_1a_spss  %>%
  summarise(total.tradeoff = sum(tradeoff), total.location = sum(location))
```

> Higher-income participants were more likely than lower-income participants to name location as the main consideration, β = 2.52, Wald-test χ2(1, N = 102) = 5.54, p < .05,...

```{r}
logit1logses <- glm(location ~ logses, data = clean_1a, family = "binomial")
summary(logit1logses)

wald.test(b = coef(logit1logses), Sigma = vcov(logit1logses), Terms = 2)
```

> but lower-income participants were more likely than higher- income participants to name trade-offs as the main con- sideration, β = −1.62, Wald-test χ2(1, N = 102) = 4.67, p <.05...

```{r}
logit2logses <- glm(tradeoff ~ logses, data = clean_1a, family = "binomial")
summary(logit2logses)

wald.test(b = coef(logit2logses), Sigma = vcov(logit2logses), Terms = 2)
```

```{r echo = FALSE}
figure1alow <- clean_1a %>%
  filter(income2 <= 35000) %>%
  mutate(total.n = n(), total.tradeoff = sum(tradeoff), prop.tradeoff = sum(tradeoff)/n(), total.location = sum(location), prop.location = sum(location)/n(), SE.tradeoff = sqrt(prop.tradeoff * (1 - prop.tradeoff)/total.n), CI.tradeoff = qnorm(.975) * SE.tradeoff, SE.location = sqrt(prop.location * (1 - prop.location)/total.n), CI.location = qnorm(.975) * SE.location) %>%
  distinct(prop.tradeoff, prop.location, CI.tradeoff, CI.location)
#computes new variables for proportion of answers, standard errors, and 95% confidence intervals for lower income group


figure1ahigh <- clean_1a %>%
    filter(income2 > 35000) %>%
  mutate(total.n = n(), total.tradeoff = sum(tradeoff), prop.tradeoff = sum(tradeoff)/n(), total.location = sum(location), prop.location = sum(location)/n(), SE.tradeoff = sqrt(prop.tradeoff * (1 - prop.tradeoff)/total.n), CI.tradeoff = qnorm(.975) * SE.tradeoff,  SE.location = sqrt(prop.location * (1 - prop.location)/total.n), CI.location = qnorm(.975) * SE.location) %>%
  distinct(prop.tradeoff, prop.location, CI.tradeoff, CI.location)
#computes new variables for proportion of answers, standard errors, and 95% confidence intervals for higher income group

title = factor(c("trade-offs", "location"), levels = c("trade-offs", "location"))
values = c(figure1alow$prop.tradeoff, figure1alow$prop.location, figure1ahigh$prop.tradeoff, figure1ahigh$prop.location)
income = c("lower income", "lower income", "higher income", "higher income")
CIs = c(figure1alow$CI.tradeoff, figure1alow$CI.location, figure1ahigh$CI.tradeoff, figure1ahigh$CI.location)
fig1a.table <- data.frame(title, values, income, CIs)
income.factor <- factor(fig1a.table$income, levels = c("lower income", "higher income"))
#figure 1a data frame (+ income.factor reverses the default position dodge of the bars)

figure1a <- fig1a.table %>%
  ggplot(aes(x = title, y = values, fill = income.factor)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("Proportion Endorsing Reason") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1a - the proportion of lower- and higher-income participants\nciting trade-off and location considerations in Study 1a\n(error bars represent 95% confidence interval)") + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1a

print(figure1a)
#displays figure 1a
```

-----

### Study 1b

> In Study 1b, there were 151 participants (median household size = 3 people, median household income = $45000). We were unable to replicate sex breakdown and mean age of participants as this data was not provided in the released dataset.

```{r echo = FALSE}
setwd("framing")
raw_1b_spss <- read.spss("study_1b.sav", to.data.frame = TRUE)
#read in the data for 1b using the spss file - the warning that comes up is okay - the data imports cleanly.

raw_1b_spss %>%
  summarise(sample.size = n(), median.household.income = median(income2), median.household.size = median(house))
```

> In Study 1b, 2 participants were excluded whose Willing-to-pay (WTP) was more than 3 standard deviations from the mean. Higher-income participants showed the classic effect, offering a higher price for beer from the resort compared to the grocery store.

```{r echo = FALSE}

clean_1b <- raw_1b_spss %>%
  filter(filter_. != "Not Selected")

clean_1b %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates high-income WTP beer price at resort - summarise to display in print-out

clean_1b_high_resort <- clean_1b %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for high income participants in the resort scenario - to use in figure 1b

clean_1b %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates high-income WTP beer price at grocer - summarise to display in print-out

clean_1b_high_grocer <- clean_1b %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for high income participants in the grocer scenario - to use in figure 1b
```

> But lower income participants' WTP did not differ significantly between beer from the resort and beer from the store.

```{r echo = FALSE}
clean_1b %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates low income WTP beer price at resort

clean_1b_low_resort <- clean_1b %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for low income participants in the resort scenario - to use in figure 1b

clean_1b %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.beer = mean(beer), CI.low = mean(beer) -  (1.96 * Sem(beer)), CI.high = mean(beer) + (1.96 * Sem(beer)))
#1.96 * standard error gives 95% CI in one direction
#this calculates low income WTP beer price at grocery store

clean_1b_low_grocer <- clean_1b %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.beer = mean(beer), CI = (1.96 * Sem(beer))) %>%
  distinct(mean.beer, CI)
#generates mean and CI for low income participants in the grocer scenario - to use in figure 1b
```

> The interaction between income and context was significant F(1,145) = 11.18, p < 0.01, eta squared partial = 0.07. (SEE FIGURE 1b)

```{r}
aov_1b <- aov(beer ~ resort * split, data = clean_1b)
summary(aov_1b)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1b, type = 2, anova = FALSE)
```

> The interaction was also significant when income was treated as a continuous variable beta = 2.27 **(the closest I could replicate from the data was 2.67)**, t(145) = 2.17, p < 0.05.

```{r}
lm1 <- lm(beer ~ resort * logses, data = clean_1b)
summary(lm1)
```

```{r echo = FALSE}
title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1b_low_grocer$mean.beer, clean_1b_high_grocer$mean.beer, clean_1b_low_resort$mean.beer, clean_1b_high_resort$mean.beer)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1b_low_grocer$CI, clean_1b_high_grocer$CI, clean_1b_low_resort$CI, clean_1b_high_resort$CI)
fig1b.table <- data.frame(title, values, location, CIs)
#figure 1b data frame

figure1b <- fig1b.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1b - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1b\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1b

print(figure1b)
#displays figure 1b
```

---

### Study 1c

> We replicated the results of 1b with larger samples in studies 1c and 1d.  In study 1c, we excluded 2 participants with missing responses, 5 with unreasonably high WTPs (over $100), and 19 additional outliers on WTP, which left 578 participants.

```{r echo = FALSE}
setwd("framing")
raw_1c_spss <- read.spss("study_1c.sav", to.data.frame = TRUE)
#read in the data for 1c using the spss file - the warning that comes up is okay - the data imports cleanly.

clean_1c <- raw_1c_spss %>%
  filter(filter_. != "Not Selected")
```

> Dividing participants according to a median split on income, we found that higher-income participants offered a higher price for beer from the resort than for beer from the grocery store:

```{r echo = FALSE}
clean_1c %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.pay = mean(pay), CI.low = mean(pay) -  (1.96 * Sem(pay)), CI.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_high_resort <- clean_1c %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for high income participants in the resort scenario - to use in figure 1c

clean_1c %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.pay = mean(pay), CI.low = mean(pay) -  (1.96 * Sem(pay)), CI.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_high_grocer <- clean_1c %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for high income participants in the grocer scenario - to use in figure 1c
```

> Lower-income participants' WTP did not differ significantly between beer from the resort, and beer from the store.

```{r echo = FALSE}
clean_1c %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.pay = mean(pay), CI.low = mean(pay) -  (1.96 * Sem(pay)), CI.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_low_resort <- clean_1c %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for low income participants in the resort scenario - to use in figure 1c

clean_1c %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.pay = mean(pay), CI.low = mean(pay) -  (1.96 * Sem(pay)), CI.high = mean(pay) + (1.96 * Sem(pay)))

clean_1c_low_grocer <- clean_1c %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.pay = mean(pay), CI = (1.96 * Sem(pay))) %>%
  distinct(mean.pay, CI)
#generates mean and CI for low income participants in the grocer scenario - to use in figure 1c
```

> The interaction between income and context was significant, F(1,574) = 5.68, p < 0.05, eta squared partial = 0.01. (SEE FIGURE 1c)

```{r}
aov_1c <- aov(pay ~ resort * split, data = clean_1c)
summary(aov_1c)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1c, type = 2, anova = FALSE)
```

> The interaction was also significant when income was treated continuously, beta = 1.65 **(the closest I could replicate was 2.03)**, t(574) = 3.27, p < 0.01.

```{r}
lm2 <- lm(pay ~ resort * logses, data = clean_1c)
summary(lm2)
```

```{r echo = FALSE}
title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1c_low_grocer$mean.pay, clean_1c_high_grocer$mean.pay, clean_1c_low_resort$mean.pay, clean_1c_high_resort$mean.pay)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1c_low_grocer$CI, clean_1c_high_grocer$CI, clean_1c_low_resort$CI, clean_1c_high_resort$CI)
fig1c.table <- data.frame(title, values, location, CIs)
#figure 1c data frame

figure1c <- fig1c.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1c - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1c\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1c

print(figure1c)
#displays figure 1c
```

-----

### Study 1d

```{r echo = FALSE}
setwd("framing")
raw_1d_spss <- read.spss("study_1d.sav", to.data.frame = TRUE)
#reads the data for study 1d

clean_1d <- raw_1d_spss %>%
  filter(filter_. != "Not Selected")
```

> In Study 1d (the nationally representative sample), a large number of participants reported unreasonably high WTPs, and exclusions based on the rules set for the smaller samples in previous studies would have left many unreasonable prices in the data set.  We therefore included in our analyses only those participants with a WTP of $20 or less, which seemed like the upper bound of a reasonable price.  This set a cutoff price similar to the cutoff price based on the stand deviations in Studies 1b and 1c. After this exclusion and the exclusion of 4 additional participants who were outlines on income, the final sample included 1,898 participants. Dividing participants according to a median split on eincome, we found that higher-income participants offered a higher price for feer from the resort (M = $6.80, 95% CI [$6.41, $7.18])

```{r echo = FALSE}
clean_1d %>%
  filter(split == 1, resort == 1) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_high_resort <- clean_1d %>%
  filter(split == 1, resort == 1) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

> than for beer from the grocery store (M = $5.46, 95% CI [$5.13, $5.79]).

```{r echo = FALSE}
clean_1d %>%
  filter(split == 1, resort == 0) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_high_grocer <- clean_1d %>%
  filter(split == 1, resort == 0) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

> Lower-income participants' WTP did not differ significantly between the resort (M = $6.21, 95% CI [$5.83, $6.60])

```{r echo = FALSE}
clean_1d %>%
  filter(split == 0, resort == 1) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_low_resort <- clean_1d %>%
  filter(split == 0, resort == 1) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

> and the store (M = %5.71, 95% CI [$5.31, $6.11]).

```{r echo = FALSE}
clean_1d %>%
  filter(split == 0, resort == 0) %>%
  summarise(mean.wtp = mean(wtp), CI.low = mean(wtp) -  (1.96 * Sem(wtp)), CI.high = mean(wtp) + (1.96 * Sem(wtp)))

clean_1d_low_grocer <- clean_1d %>%
  filter(split == 0, resort == 0) %>%
  mutate(mean.wtp = mean(wtp), CI = (1.96 * Sem(wtp))) %>%
  distinct(mean.wtp, CI)
```

> The interaction between income and context was significant, F(1, 1984) = 4.82, p < 0.05, eta squared partial = 0.003. (SEE FIGURE 1d)

```{r echo}
aov_1d <- aov(wtp ~ resort * split, data = clean_1d)
summary(aov_1d)
#they ran this anova on the binary 'split' column?

etaSquared(aov_1d, type = 2, anova = FALSE)
```

> This interaction was marginally significant when income was treated continuously, beta = 0.50 **(the closest I could replicate was 0.93)**, t(1894) = 1.85, p < 0.07.

```{r}
lm3 <- lm(wtp ~ resort * logses, data = clean_1d)
summary(lm3)
```

```{r echo = FALSE}
title = factor(c("Lower Income", "Higher Income"), levels = c("Lower Income", "Higher Income"))
values = c(clean_1d_low_grocer$mean.wtp, clean_1d_high_grocer$mean.wtp, clean_1d_low_resort$mean.wtp, clean_1d_high_resort$mean.wtp)
location = c("Grocer", "Grocer", "Resort", "Resort")
CIs = c(clean_1d_low_grocer$CI, clean_1d_high_grocer$CI, clean_1d_low_resort$CI, clean_1d_high_resort$CI)
fig1d.table <- data.frame(title, values, location, CIs)
#figure 1c data frame

figure1d <- fig1d.table %>%
  ggplot(aes(x = title, y = values, fill = location)) + geom_bar(stat = "identity", position = position_dodge(), colour = "black") + ylab("WTP (dollars)") + xlab(NULL) + geom_errorbar(aes(ymin = values - CIs, ymax = values + CIs), width = 0.2, position = position_dodge(0.9)) + theme_bw() + scale_fill_grey(start = .3, end = .85) + ggtitle("Figure 1d - Amount participants were willing to pay (WTP)\nfor beer at the grocery store and resort in Study 1d\n(error bars represent 95% confidence interval)") + scale_y_continuous(breaks = seq(0, 8, 1)) + theme(panel.border = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
#produces figure 1d

print(figure1d)
#displays figure 1d
```

-----

### Study 2a 

```{r echo = FALSE}
setwd("framing")
raw_2a_spss <- read.spss("study_2a.sav", to.data.frame = TRUE)
#reads the data for study 2a
```

> In Study 2a, there were 238 participants ((we are unable to replicate mean age, gender split, median household size, or median household income due to that data not being in the public dataset)) Median ses (which is income / sqrt(householdsize)):

```{r echo = FALSE}
raw_2a_spss %>%
  summarise(sample.size = n(), median.ses = median(ses))
```

> One participant was excluded as an outlier on income.

```{r echo = FALSE}
# Filter out outlier
clean_2a <- raw_2a_spss %>%
  filter(filter_. != "Not Selected")
```

> We conducted binary logistic regressions to comepare the frequency with which participants cited each of the two considerations of interest (trade-offs vs proportional discount) as a function of income.  Higher-income participants were more likely than lower-income participants to use proportional thinking, beta = 0.87, Wald-test chi square (1, N = 237) = 4.02, p < 0.05.

```{r}
logit3logses <- glm(context ~ lgses, data = clean_2a, family = "binomial")
summary(logit3logses)

wald.test(b = coef(logit3logses), Sigma = vcov(logit3logses), Terms = 2)
```

> but lower-income participants were more likely than higher-income participants to use trade-off thinking, beta = -0.96, Wald-test chi square (1, N = 237) = 4.69, p < 0.05.

```{r}
logit4logses <- glm(tradeoff ~ lgses, data = clean_2a, family = "binomial")
summary(logit4logses)

wald.test(b = coef(logit4logses), Sigma = vcov(logit4logses), Terms = 2)
```

--- 

### Study 2b

```{r echo = FALSE}
setwd("framing")
raw_2b_spss <- read.spss("study_2b.sav", to.data.frame = TRUE)
#reads the data for study 2b
```

> In Study 2b, there were 705 participants ((could not replicate mean age or gender split since that data is not included in the public dataset)), (median household size = 3 people, median household income = $45,000).

```{r echo = FALSE}
raw_2b_spss %>%
  summarise(sample.size = n(), median.household.size = (median(house)), median.income = median(inc2))
```

> In Study 2b, 1 participant was excluded for missing responses, and 2 were excluded as outliers on income.

```{r echo = FALSE}
clean_2b <- raw_2b_spss %>%
  filter(filter_. != "Not Selected", go != "NA")
```

> The analyses conducted were based on a median split on income.  Confirming earlier findings, these analyses revealed that higher-income participants were more willing to travel when the discount was proportionally larger (i.e., the tablet cost less): Specifically, 86%, 75%, and 58% would travel when the tablet cost $300, $500, and $1,000, respectively.

```{r echo = FALSE}
clean_2b %>%
  filter(split == 1, cond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2b %>%
  filter(split == 1, cond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2b %>%
  filter(split == 1, cond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

> Lower-income participants were less sensitive to the proportional size of the discount: The corresponding percentages of lower-income participants willing to travel were 78%, 67%, and 67%.

```{r echo = FALSE}
clean_2b %>%
  filter(split == 0, cond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2b %>%
  filter(split == 0, cond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2b %>%
  filter(split == 0, cond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

> The ineraction between income and context was significant in a binary logistic regression, beta = -0.048, Walt-test chi square (1, N = 702) = 4.93, p < 0.05,

```{r}
logit5logses <- glm(go ~ split * cond, data = clean_2b, family = "binomial")
summary(logit5logses)

wald.test(b = coef(logit5logses), Sigma = vcov(logit5logses), Terms = 4)
```

> and was marginally significant when income was treated continuously, beta = -0.57, Wald-test chi square(1, N - 702) = 3.32, p < 0.07.

```{r}
logit6logses <- glm(go ~ logses * cond, data = clean_2b, family = "binomial")
summary(logit6logses)

wald.test(b = coef(logit6logses), Sigma = vcov(logit6logses), Terms = 4)
```

### Study 2c

> Five participants were excluded for missing responses in Study 2c, so 1,893 participants were included in the analyses.

```{r echo = FALSE}
# read data in
setwd("framing")
raw_2c_spss <- read.spss("study_1d.sav", to.data.frame = TRUE)
#reads the data for study 2c

clean_2c <- raw_1d_spss %>%
  filter(filter_. != "Not Selected", go != "NA")
```

> Analyses based to a median split on income revealed a more muted trend than in the previous study.  Among higher-income participants, 71%, 67%, and 51% were willing to travel when the tablet cost $300, $500, and $1,000, respectively;

```{r echo = FALSE}
clean_2c %>%
  filter(split == 1, webercond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 1, webercond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 1, webercond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

> among lower-income participants, the corresponding percentages were 70%, 69%, and 55%.

```{r echo = FALSE}
clean_2c %>%
  filter(split == 0, webercond == 0) %>%
  summarise(threehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 0, webercond == 1) %>%
  summarise(fivehundred_go = (sum(go) / n()) * 100)

clean_2c %>%
  filter(split == 0, webercond == 2) %>%
  summarise(onethousand_go = (sum(go) / n()) * 100)
```

> When income was treated continuously, the interaction between income and context was clear, beta = -0.39, Wald-test chi square(1, N = 1,893) = 6.13, p < 0.05.

```{r}
logit7logses <- glm(go ~ logses * webercond, data = clean_2c, family = "binomial")
summary(logit7logses)

wald.test(b = coef(logit7logses), Sigma = vcov(logit7logses), Terms = 4)
```

---

### Study 2d 

> In Study 2d, there were 301 participants (mean age = 30.2 years; 120 females, 181 males; median household size = 3 people; median household income = $25,000).

```{r echo=F}
# Read data in
df2d_1 <- read.csv("csv_files/2d_Sheet1.csv", header=T)
df2d_2 <- read.csv("csv_files/2d_Sheet2.csv", header=T)
```

```{r echo=F}
# Number of subjects
df2d_1 %>%
  select(subject) %>%
  summarise(n())

# Mean age
df2d_2 %>%
  summarise(mean(age, na.rm=T)) %>%
  round(digits=1)

# Number of females vs. males
df2d_2 %>%
  group_by(gender) %>%
  summarise(n())
```

*Attempt to replicate median household size was complex:*

```{r}
# Median Household Size
# calculated using income2 : doesn't match
df2d_1 %>%
  summarize(median(inc2, na.rm=T))
# calculated using ses : doesn't match
df2d_1 %>%
  summarize(median(ses, na.rm=T)) %>%
  round(digits=0)
# calculated using income (converted) then inverted : matches!
df2d_1 %>%
  summarize(median(income, na.rm=T))
df2d_1 %>%
  select(inc2) %>%
  distinct() %>%
  arrange(inc2) %>%
  slice(3) # '3' derived from above
# Note above: (technical) I tried to, but couldn't figure out how to use a variable instead of explicitly using the value 3. Again, I suspected the median was taken from the categorized income and then backward matched to its raw value. I suspect this is erroneous and probably due to disregarding the categorical value of 0 is meaningful.
```

> Results: We regressed willingness to travel on income (categorized by a median split), proportional size of the discount (large vs. small), absolute size of the discount ($10 vs. $150), all two-way interaction terms, and the three-way interaction term. 

```{r eval=F}
# Regression
glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")
```

Assumptions:

* willingness = 'go'
* income with median split = 'split'
* proportionate discount = 'lgdiscount'
* abs size discount = 'lgsavings'

> Higher-income participants were significantly more willing to travel for a proportionally larger discount (60%) than for a proportionally smaller discount (41%), but this was not true for lower-income participants (50% vs. 61%). 

```{r echo=FALSE}
# high-income & proportionately larger discount
df2d_1 %>%
  filter(split == 1, lgdiscount == 0) %>%
  summarise(high_prop_large = (sum(go) / n()) * 100) %>%
  round(digit=0)

# high-income & proprotionately smaller discount
df2d_1 %>%
  filter(split == 1, lgdiscount == 1) %>%
  summarise(high_prop_small = (sum(go) / n()) * 100) %>%
  round(digit=0)

# low-income & proprotionately larger discount
df2d_1 %>%
  filter(split == 0, lgdiscount == 0) %>%
  summarise(high_prop_large = (sum(go) / n()) * 100) %>%
  round(digit=0)

# low-income & proprotionately smaller discount
df2d_1 %>%
  filter(split == 0, lgdiscount == 1) %>%
  summarise(high_prop_small = (sum(go) / n()) * 100) %>%
  round(digit=0)
```

> The interaction between proportional discount and income was significant, β = −1.90, Wald-test χ2(1, N = 301) = 4.11, p < .05. 

```{r echo=F}
temp.model <- glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")

# β (beta), p
glm(go ~ split*lgdiscount*lgsavings, 
    data = df2d_1, family = "binomial") %>% 
  tidy() %>%
  filter(term == "split:lgdiscount") %>%
  mutate(β = round(estimate, digit = 2),
         p = round(p.value, digit = 2)) %>%
  select(term, β, p)

# wald test
print(wald.test(b = coef(temp.model), 
                Sigma = vcov(temp.model), 
                Terms = 5)$result$chi2[1], digit = 3)
```

> Note that this interaction did not depend on the absolute amount of the discount, as the three-way interaction was not significant, β = −0.89, Wald-test χ2(1, N = 301) = 0.28, p > .6. 

```{r echo=F}
temp.model <- glm(go ~ split*lgdiscount*lgsavings, data = df2d_1, family = "binomial")

# β (beta), p
glm(go ~ split*lgdiscount*lgsavings, 
    data = df2d_1, family = "binomial") %>% 
  tidy() %>%
  filter(term == "split:lgdiscount:lgsavings") %>%
  mutate(β = round(estimate, digit = 2),
         p = round(p.value, digit = 4)) %>%
  select(term, β, p)

# wald test
print(wald.test(b = coef(temp.model), 
                Sigma = vcov(temp.model), 
                Terms = 8)$result$chi2[1], digit = 3)
```

> When income was treated continuously, the interaction between proportional discount and income also emerged, but was not significant, β = −2.13, Wald-test χ2(1, N = 301) = 2.21, p < .15.

**^ Failed to replicate**

```{r echo=F, eval=F}
## Gaussian link function:
# instead of split, use income : doesn't match
tidy(glm(go ~ income*lgdiscount*lgsavings, data = df2d_1, family = "gaussian"))[5,]
# instead of split, use inc2 : doesn't match
tidy(glm(go ~ inc2*lgdiscount*lgsavings, data = df2d_1, family = "logses"))[5,]
# instead of split, use ses : doesn't match
tidy(glm(go ~ ses*lgdiscount*lgsavings, data = df2d_1, family = "gaussian"))[5,]

## Tried Binomial link function: 
# instead of split, use income : doesn't match
tidy(glm(go ~ income*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]
# instead of split, use inc2 : doesn't match
tidy(glm(go ~ inc2*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]
# instead of split, use ses : doesn't match
tidy(glm(go ~ ses*lgdiscount*lgsavings, data = df2d_1, family = "binomial"))[5,]

## Random attempt:
# p matches : 0.145, but nothing else
tidy(glm(go ~ inc2:lgdiscount, data = df2d_1, family = "gaussian"))

# wald test : haven't because I don't know which model to use
```

---

### Study 3

> In Study 3, there were 505 participants (mean age = 33.0 years; 208 females, 297 males; median household size = 3 people; median household income = $45,000).

```{r echo=F}
# Read data in
df3_1 <- read.csv("csv_files/3_Sheet1.csv", header=T)
df3_2 <- read.csv("csv_files/3_Sheet2.csv", header=T)
```

```{r echo=F}
# Number of subjects
df3_1 %>%
  select(Subject) %>%
  summarise(n())

# Mean age
df3_2 %>%
  summarise(mean(age, na.rm=T)) %>%
  round(digits=1)

# Number of females vs. males
df3_2 %>%
  group_by(gender) %>%
  summarise(n())

# Median household size
df3_1 %>%
  summarize(median(house))

# Median household income
df3_1 %>%
  summarize(median(inc2))
```

> One participant was excluded for missing responses, and another was excluded as an outlier on income. 

``` {r echo=F}
# remove participant with missing response
df3_1 <- df3_1 %>%
  filter(!is.na(judge))

# look for outlier in income (ses)
df3_1 %>%
  arrange(desc(ses)) %>%
  tbl_df

# remove outlier (subject 14)
df3_1 <- df3_1 %>%
  filter(Subject!=14)
```

> Analyses based on a median split on income replicated earlier results. Higher-income individuals rated the loss gamble as significantly more attractive (M = 11.63, 95% CI = [10.56, 12.69]) than the no-loss gamble (M = 8.33, 95% CI = [7.62, 9.04]), but this difference was smaller for lower-income individuals (loss gamble: M = 10.38, 95% CI = [9.38, 11.38], no-loss gamble: M = 9.18, 95% CI = [8.31, 10.05]).

Assumptions:

* Higher-income (via median split) : split = 1
* Lower-income (via median split) : split = 0
* Loss gamble : cond = 1
* No-loss gamble : cond = 0
* attractive rating : judge

Numbers are fractionally different...

```{r echo=F}
# high-income & loss gambling : attractive rating
temp_title <- "High-income & Loss gambling : attractive rating"
temp_x <- df3_1 %>%
  filter(split==1, cond==1) %>%
  select(judge)
Mean_CI(temp_title, temp_x) # print

# high-income & no-loss gambling : attractive rating
temp_title <- "High-income & No-loss gambling : attractive rating"
temp_x <- df3_1 %>%
  filter(split==1, cond==0) %>%
  select(judge)
Mean_CI(temp_title, temp_x) # print

# low-income & loss gambling : attractive rating
temp_title <- "Low-income & Loss gambling : attractive rating"
temp_x <- df3_1 %>%
  filter(split==0, cond==1) %>%
  select(judge)
Mean_CI(temp_title, temp_x) # print

# low-income & no-loss gambling : attractive rating
temp_title <- "Low-income & No-loss gambling : attractive rating"
temp_x <- df3_1 %>%
  filter(split==0, cond==0) %>%
  select(judge)
Mean_CI(temp_title, temp_x) # print
```

> The interaction between gamble and income was significant, F(1, 499) = 5.04, p < .05, ηp2 = .01.

```{r}
# ANOVA : interaction effects
# income treated as split : somewhat matches
summary(aov(judge ~ split*cond, df3_1))
temp_eta2 <- etaSquared(aov(judge ~ split*cond, df3_1)) %>%
  .[3,2] %>%
  round(digit=2)
print(c("ηp2:", temp_eta2), quote=F)
```

> The interaction was also significant when income was treated continuously, β = 1.13, t(499) = 2.21, p < .05. 

**^ replication is close; not different enough to effect significance**

```{r}
# when income is treated continuously as inc2 : matches even less
summary(glm(judge ~ inc2*cond, df3_1, family=gaussian))
```

---

### Study 4

> In Study 4, there were 263 participants (mean age = 31.6 years; 102 females, 161 males; median household size = 3 people; median household income = $45,000).

```{r echo=F}
# Read data in
df4_1 <- read.csv("csv_files/4_Sheet1.csv", header=T)
df4_2 <- read.csv("csv_files/4_Sheet2.csv", header=T)
df4_4 <- read.csv("csv_files/4_Sheet4.csv", header=T)
```

```{r echo=F}
# Number of subjects
df4_2 %>%
  select(Subject) %>%
  summarise(n())

# Mean age
df4_2 %>%
  summarise(mean(Age, na.rm=T)) %>%
  round(digits=1)

# Number of females vs. males
df4_2 %>%
  group_by(Gender) %>%
  summarise(n())

# Median household size
df4_2 %>%
  summarize(median(House))

# Median household income
df4_1 %>%
  summarize(median(Income2))
```

> Four participants were excluded for not completing the prime question.

```{r echo=F}
# find the four participants excluded
df4_4 %>%
  filter(Prime=="") %>%
  select(Subject)
# remove the 4 participants
df4_1 <- df4_1 %>%
  filter(Subject!=56, Subject!=75, Subject!=112, Subject!=236)
```

> When we analyzed the data using a median split based on income, higher-income participants rated the DVD as significantly more expensive when they thought about a small account (M = 5.74, 95% CI = [5.04, 6.44]) rather than a large account (M = 4.47, 95% CI = [3.93, 5.01]), whereas the evaluations of lower-income participants did not differ significantly between the conditions (small account: M = 5.55, 95% CI = [4.92, 6.18]; large account: M = 5.75, 95% CI = [5.03, 6.48]).

Assumptions:

* Higher-income : Split = 1
* Lower-income : Split = 0
* Small Account : Large.Acc = 0
* DVD expensiveness : Expense

```{r echo=F}
# high-income & small account : expensiveness
temp_title <- "High-income & Small account : expensiveness"
temp_x <- df4_1 %>%
  filter(Large.Acc==0, Split==1) %>%
  select(Expense)
Mean_CI(temp_title, temp_x) # print

# high-income & large account : expensiveness
temp_title <- "High-income & Large account : expensiveness"
temp_x <- df4_1 %>%
  filter(Large.Acc==1, Split==1) %>%
  select(Expense)
Mean_CI(temp_title, temp_x) # print

# low-income & small account : expensiveness
temp_title <- "Low-income & Small account : expensiveness"
temp_x <- df4_1 %>%
  filter(Large.Acc==0, Split==0) %>%
  select(Expense)
Mean_CI(temp_title, temp_x) # print

# low-income & large account : expensiveness
temp_title <- "Low-income & Large account : expensiveness"
temp_x <- df4_1 %>%
  filter(Large.Acc==1, Split==0) %>%
  select(Expense)
Mean_CI(temp_title, temp_x) # print
```

> The interaction between income and condition was significant, F(1, 255) = 4.96, p < .05, ηp2 = .02....

```{r}
# ANOVA : interaction effects
# income treated as split : replicates
summary(aov(Expense ~ Large.Acc*Split, df4_1))
temp_eta2 <- etaSquared(aov(Expense ~ Large.Acc*Split, df4_1)) %>%
  .[3,2] %>%
  round(digit=2)
print(c("ηp2:", temp_eta2), quote=F)
```

> The interaction was also significant when income was treated as a continuous variable, β = 2.43, t(255) = 3.39, p < .01. 

**^ as a continuous variable, failure to replicate**

```{r}
# when income is treated continuously as Income2 : doesn't replicate
summary(glm(Expense ~ Large.Acc*Income2, df4_1, family=gaussian))

# Multinomal regression : using package : nnet
# multinom(Expense ~ Large.Acc*Income2, data = df4_1)
```

---

### Study 5

> In Study 5, there were 234 participants (mean age = 31.8 years; 107 females, 127 males)

```{r echo=F}
# Read data in
df5_demo <- read.csv("csv_files/5_demo.csv", header=T)
df5_1 <- read.csv("csv_files/5_Sheet1.csv", header=T)
```

```{r echo=F}
# Number of subjects
df5_demo %>%
  select(subject) %>%
  summarise(n())

# Number of females vs. males
df5_demo %>%
  group_by(gender) %>%
  summarise(n())
```

> No participants were excluded from the analyses. We first analyzed responses using a median split on participants’ dieting behavior. Nondieters rated the fries as more fattening when they thought about a small account (M = 8.64, 95% CI = [8.20, 9.07]) than when they thought about a large account (M = 7.80, 95% CI = [7.21, 8.38]), but this was not true for dieters (small account: M = 8.86, 95% CI = [8.29, 9.43]; large account: M = 9.13, 95% CI = [8.66, 9.60]).

Assumptions:

* Dieters : split = 1
* Nondieters : split = 0
* Small Account : large = 0
* Large Account : large = 1
* Fattening : fat

```{r echo=F}
# Nondieters & Small account : Fattening
temp_title <- "Nondieters & Small account : Fattening"
temp_x <- df5_1 %>%
  filter(split==0, large==0) %>%
  select(fat)
Mean_CI(temp_title, temp_x) # print

# Nondieters & Large account : Fattening
temp_title <- "Nondieters & Large account : Fattening"
temp_x <- df5_1 %>%
  filter(split==0, large==1) %>%
  select(fat)
Mean_CI(temp_title, temp_x) # print

# Dieter & Small account : Fattening
temp_title <- "Dieter & Small account : Fattening"
temp_x <- df5_1 %>%
  filter(split==1, large==0) %>%
  select(fat)
Mean_CI(temp_title, temp_x) # print

# Dieter & Large account : Fattening
temp_title <- "Dieter & Large account : Fattening"
temp_x <- df5_1 %>%
  filter(split==1, large==1) %>%
  select(fat)
Mean_CI(temp_title, temp_x) # print
```

> The interaction between dieting status and condi- tion was significant, F(1, 230) = 4.40, p < .05, ηp2 = .02, and the...

```{r}
# ANOVA : interaction effects
# income treated as split : somewhat matches
summary(aov(fat ~ split*large, df5_1))
temp_eta2 <- etaSquared(aov(fat ~ split*large, df5_1)) %>%
  .[3,2] %>%
  round(digit=2)
print(c("ηp2:", temp_eta2), quote=F)
```

> interaction was also found when dieting behavior was treated continuously, β = 0.43, t(230) = 2.11, p < .05. ...

**^ can't replicate continous because no continous variable provided..**

```{r}
# when income is treated continuously
# note: no proper continuous income variable included in open dataset
# can't replicate
summary(lm(fat ~ split*large, df5_1))
```

---

### Study 6

> In Study 6, 74 participants (mean age = 32.0 years; 46 females, 28 males) were...

```{r echo=F}
df6_demo <- read.csv("csv_files/6_demo.csv", header=T)
df6_raw <- read.csv("csv_files/6_raw.csv", header=T)
df6_cric <- read.csv("csv_files/6_cric.csv", header=T)
```

```{r echo=F}
# Number of subjects
df6_demo %>%
  select(Subject) %>%
  summarise(n())

# Mean age
df6_demo %>%
  summarise(mean(Age, na.rm=T)) %>%
  round(digit=1)

# Number of females vs. males
df6_demo %>%
  group_by(Gender) %>%
  summarise(n())
```

> One participant was excluded because of a computer malfunction during the game. 

```{r}
# participant 16 deduced from SPSS
df6_cric <- df6_cric %>%
  filter(Subject!='16')
df6_cric %>%
   summarise(n_distinct(Subject)) 
```

> Time-rich participants rated the loss as more expensive when they thought about a small account (M = 8.31, 95% CI = [7.78, 8.84]) than when they thought about a large account (M = 6.50, 95% CI = [5.42, 7.58]), whereas time-poor participants’ evaluations did not differ between the small-account condition (M = 8.33, 95% CI = [7.14, 9.52]) and the large- account condition (M = 8.83, 95% CI = [7.97, 9.69]).

Assumptions:

*Time-rich : Slack = 1
*Time-poor : Slack = 0
*Small account : Large = 0
*Large account : Large = 1
*Expensive : expense

```{r}
# Time-rich & Small account: Expensive
temp_title <- "Time-rich & Small account: Expensive"
temp_x <- df6_cric %>%
  filter(Slack==1, Large==0) %>%
  select(expense)
Mean_CI(temp_title, temp_x) # print

# Time-rich & Large account: Expensive
temp_title <- "Time-rich & Large account: Expensive"
temp_x <- df6_cric %>%
  filter(Slack==1, Large==1) %>%
  select(expense)
Mean_CI(temp_title, temp_x) # print

# Time-poor & Small account: Expensive
temp_title <- "Time-poor & Small account: Expensive"
temp_x <- df6_cric %>%
  filter(Slack==0, Large==0) %>%
  select(expense)
Mean_CI(temp_title, temp_x) # print

# Time-poor & Large account: Expensive
temp_title <- "Time-poor & Large account: Expensive"
temp_x <- df6_cric %>%
  filter(Slack==0, Large==1) %>%
  select(expense)
Mean_CI(temp_title, temp_x) # print
```

> A 2 (scarcity condition) × 2 (account condition) analysis of variance revealed a significant interaction, F(1, 69) = 5.16, p < .05, ηp2 = .07.

```{r}
# ANOVA : interaction effects
# income treated as split : replicates
summary(aov(expense ~ Large*Slack, df6_cric))
temp_eta2 <- etaSquared(aov(expense ~ Large*Slack, df6_cric)) %>%
  .[3,2] %>%
  round(digit=2)
print(c("ηp2:", temp_eta2), quote=F)
```
